Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-02-21 ms/manuscript.Rmd
Update MS

```{r word-count table}
tibble(
  words = c(
    "Total word count (Introduction, Materials and Methods, Results, Discussion):_6601",
    "Summary:_199",
    "Introduction:_881",
    "Materials and Methods:_2491",
    "Results:_822",
    "Discussion:_2407",
    "Acknowledgements:_170"),
  figs_tabs = c(
    "No. of figures:_7 (all in color)",
    "No. of tables:_5",
    "No. of supporting information files:_10 (Figs. S1-S2; Tables S1-S8)", "", "", "", "")
) %>%
  separate(words, c("words", "word_count"), sep = "_") %>%
  separate(figs_tabs, c("figs", "fig_count"), sep = "_", fill = "right") %>%
  mutate_all(~replace_na(., "")) %>%
  knitr::kable(format = "latex", escape = TRUE, col.names = NULL) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "2em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "8em")
```

@@

Community-weighted mean values (CWMs) were smaller for epiphytic than terrestrial ferns for size-related traits (frond length, frond width, stipe length, and rhizome diameter) and number of pinnae pairs (\tval-test, all \pval{ }< 0.05; `r figure("cwm-div")`).
Spatial autocorrelation was detected in the linear model for SLA, so a spatial generalized mixed model was used instead (see Methods).
Specific leaf area decreased with elevation, and was slightly lower for epiphytic relative to terrestrial communities (spatial generalized linear mixed model, nu = `r sla_nu`, rho = `r sla_rho`, AIC = `r sla_AIC`; `r s_table("spatial-sla")`).
Degree of lamina dissection decreased with elevation in epiphytes, but increased in terrestrial communities (linear model, \rval^2^ = `r get_mod_result(model_summ_print, "dissection", "r")`, \pval{ }`r get_mod_result(model_summ_print, "dissection", "p")`).
Rhizome diameter decreased slightly with elevation for terrestrial communities, while increasing slightly for epiphytic communities (`r figure("cwm-div")`).

>>>>

```{r word-count table}
tibble(
  words = c(
    "Total word count (Introduction, Materials and Methods, Results, Discussion):_6603",
    "Summary:_199",
    "Introduction:_881",
    "Materials and Methods:_2491",
    "Results:_824",
    "Discussion:_2407",
    "Acknowledgements:_170"),
  figs_tabs = c(
    "No. of figures:_7 (all in color)",
    "No. of tables:_5",
    "No. of supporting information files:_10 (Figs. S1-S2; Tables S1-S8)", "", "", "", "")
) %>%
  separate(words, c("words", "word_count"), sep = "_") %>%
  separate(figs_tabs, c("figs", "fig_count"), sep = "_", fill = "right") %>%
  mutate_all(~replace_na(., "")) %>%
  knitr::kable(format = "latex", escape = TRUE, col.names = NULL) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "2em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "8em")
```

@@

Community-weighted mean values (CWMs) were smaller for epiphytic than terrestrial ferns for size-related traits (frond length, frond width, stipe length, and rhizome diameter), frond dissection, and number of pinnae pairs (\tval-test, all \pval{ }< 0.05; `r figure("cwm-div")`).
Spatial autocorrelation was detected in the linear model for SLA, so a spatial generalized mixed model was used instead (see Methods).
Specific leaf area decreased with elevation, and was slightly lower for epiphytic relative to terrestrial communities (spatial generalized linear mixed model, nu = `r sla_nu`, rho = `r sla_rho`, AIC = `r sla_AIC`; `r s_table("spatial-sla")`).
Degree of lamina dissection decreased with elevation in epiphytes, but increased in terrestrial communities (linear model, \rval^2^ = `r get_mod_result(model_summ_print, "dissection", "r")`, \pval{ }`r get_mod_result(model_summ_print, "dissection", "p")`).
Rhizome diameter decreased slightly with elevation for terrestrial communities, while increasing slightly for epiphytic communities (`r figure("cwm-div")`).
